---
title: "Model Details for farsCS"
author: "Clement Schaff"
date: "27 avril 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Model Details for farsCS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VinetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FARS DATA

FARS is a nationwide census providing NHTSA, Congress and the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. For more detail on FARS data,  <https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars>.

The  **farsCS** package provides easy summary statistics and plotting functions to deal with fars data. 

### Main functions

farsCS package gives some function to easily access and manipulate FARS data:

* fars_summarize_years returns Returns a month/year table with the number of fatalities for each month of each year.


```{r fars}
fars_summarize_years(2013:2015)
```

* fars_map_state plots fatalities on a map for a state in a given year

